The eclipse of ASASSN-21qj

### 2022-12-14 src/tex/ms.tex
[showyourwork] overleaf sync

@@

Terrestrial planets are thought to be built up by the quasi-periodic accretion of planetary embryos that generate a significant amount of ejected material.
%
The Earth's moon is believed to have formed from the resulting aftermath of a collision in the early Solar system.
%
Sudden increases of infrared flux from systems known to host debris disks indicate that this is a stochastic process that can occur on timescales of a few months or less.
%
Models of these impacts and the subsequent evolution of the dust clouds have been modeled \citep{Jackson12,Jackson14} and have been seen ar IR wavelengths \citep{Su19,Su22}.

@@

@@

TODO: to estimate the minimum mass of all the sub-micron dust in the eclipse and equate that to YYYYY kg of solid material.

@@

We first consider some scenario independent constraints, as these illustrate some basic problems which are summarised in Figure \ref{fig:constr}.
%
Most simply, the IR photometry requires very warm dust, but the delay between the IR flux increase and the optical dimming suggests material that is far from the star.
%
While there are other means than stellar luminosity to heat dust, the star is the most conventional source, and requires the dust to be at about 0.1\,au given the near-constant temperature of $\sim$1000\,K (Fig XXX). A blackbody at this temperature that fits the WISE fluxes implies a dust luminosity of 0.03\,$L_\star$; that is, assuming blackbody-like absorption and emission 0.03 of the stellar emission is absorbed and re-emitted by the dust.
%
A several-year delay between the IR flux increase and the optical transit, however, implies that the material is on an orbit with a period of at least several years, and hence several au.
%
The duration of the optical transit also suggests a distance of order an au or greater, since closer material would have a period that is shorter than the duration of the transit.
%
Finally, a large orbital distance is also suggested by the gradients in the optical light curve, though the velocities inferred from the gradients are lower limits and hence the material could be closer.

@@

\begin{figure}
    \centering
    \includegraphics[width=0.5\textwidth]{figures/fvsr.pdf}
    \caption{Model-independent constraints in terms of dust fractional luminosity ($L_{\rm dust}/L_\star$) and stellocentric radius.
    %
    The dot shows the location of the dust from an SED fit, and the curved line shows cooler dust that is consistent with the WISE W2 flux alone.
    %
    The diagonal line shows the upper limit from the ALMA non-detection.
    %
    The vertical dotted line shows an approximate lower radial limit on the dust location based on the transit duration.
    %
    The dashed line a lower radial limit based on the delay between the IR flux increase and optical transit.
    %
    The vertical solid line shows an upper radial limit based on the optical light curve gradients.}
    \label{fig:constr}
    \script{fvsr.py}
\end{figure}

>>>>

%\newcommand{\todo2}[1]{{\colorbox{yellow}{\color{red}[TODO]:#1}}}
\newcommand{\todo}[1]{
\colorbox{yellow}{
\begin{minipage}{0.8\linewidth}
\color{red}
TODO: #1
\end{minipage}
}}

@@

Terrestrial planets are thought to be built up by the quasi-periodic accretion of planetary embryos that generate a significant amount of ejected material.
%
The Earth's moon is believed to have formed from the resulting aftermath of a collision in the early Solar system.
%
Sudden increases of infrared flux from systems known to host debris disks indicate that this is a stochastic process that can occur on timescales of a few months or less.
%
Models of these impacts and the subsequent evolution of the dust clouds have been modeled \citep{Jackson12,Jackson14} and have been seen at IR wavelengths \citep{Su19,Su22}.

@@

ADD OBS DATE

@@

\todo{to estimate the minimum mass of all the sub-micron dust in the eclipse and equate that to YYYYY kg of solid material.}

@@

We first consider some scenario independent constraints, as these illustrate some basic problems which are summarised in Figure \ref{fig:constr}.
%
Most simply, the IR photometry requires very warm dust, but the delay between the IR flux increase and the optical dimming suggests material that is far from the star.
%
While there are other means than stellar luminosity to heat dust, the star is the most conventional source, and requires the dust to be at about 0.1\,au given the near-constant temperature of $\sim$1000\,K (Fig XXX). A blackbody at this temperature that fits the WISE fluxes implies a dust luminosity of 0.034\,$L_\star$; that is, assuming blackbody-like absorption and emission 0.034 of the stellar emission is absorbed and re-emitted by the dust. For a dust temperature of 1000\,K, the emitting area is 0.01\,au$^2$, equivalent to an object about 7\,$R_\odot$ in radius.
%
A several-year delay between the IR flux increase and the optical transit, however, implies that the material is on an orbit with a period of at least several years, and hence several au.
%
The duration of the optical transit also suggests a distance of order an au or greater, since closer material would have a period that is shorter than the duration of the transit.
%
Finally, a large orbital distance is also suggested by the gradients in the optical light curve, though the velocities inferred from the gradients are lower limits and hence the material could be closer.

@@

\begin{figure}
    \centering
    \includegraphics[width=0.5\textwidth]{figures/fvsr.pdf}
    \caption{Model-independent constraints in terms of dust fractional luminosity ($L_{\rm dust}/L_\star$) and stellocentric radius or temperature.
    %
    The dot shows the location of the dust from an SED fit, and the curved line shows cooler dust that is consistent with the WISE W2 flux alone. The grey line shows what could have been detected with WISE; with detectable emission at a given radius/temperature lying above the grey line.
    %
    The diagonal line shows the upper limit from the ALMA non-detection.
    %
    The vertical dotted line shows an approximate lower radial limit on the dust location based on the transit duration.
    %
    The dashed line a lower radial limit based on the delay between the IR flux increase and optical transit.
    %
    The vertical solid line shows an upper radial limit based on the optical light curve gradients.}
    \label{fig:constr}
    \script{fvsr.py}
\end{figure}
